Clines from PDE

### 2016-02-05 notes/pde-clines.Rmd
comparison to theory; changed "F" to "FALSE"
comparison to theory progressing

xgrid <- setup.grid.1D(x.up=-20, x.down=20, N=10)
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=40)

# took 24min with xgrid$N=10, rgrid$N=20 and 50 time steps up to t=3, :(
hap.soln <- forwards_backwards_haplotypes(s=s, times=tt, xgrid=xgrid, rgrid=rgrid)
```

>>>>

xgrid <- setup.grid.1D(x.up=-20, x.down=20, N=21)
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=40)

hap.soln <- forwards_backwards_haplotypes(s=s, times=tt, xgrid=xgrid, rgrid=rgrid)
```
